### 2023-04-26 chapter2/chapter2.tex
Added paragraph motivating use of Drosophila

%    B. Though other analyses have identified Though IDRs short linear motifs (SLiMs) are enriched in IDRs and are sometimes strongly conserved at specific positions, these residues constitute a small fraction of disordered regions. However, because these motifs are short and some are highly permissive at specific positions, they have high evolutionarily plasticity. Thus, motifs

%Though these motifs are sometimes conserved by position and can be identified as short segments of conservation in otherwise highly diverged alignments of IDRs, their brief lengths make them evolutionarily plastic. Thus, they are easily

@@

>>>>

% This form of constraint is    B. Though other analyses have identified Though IDRs short linear motifs (SLiMs) are enriched in IDRs and are sometimes strongly conserved at specific positions, these residues constitute a small fraction of disordered regions. However, because these motifs are short and some are highly permissive at specific positions, they have high evolutionarily plasticity. Thus, motifs
%Though these motifs are sometimes conserved by position and can be identified as short segments of conservation in otherwise highly diverged alignments of IDRs, their brief lengths make them evolutionarily plastic. Thus, they are easily

@@

However, no known subsequent studies have determined if similar patterns of conservation are found in the IDRs of other systems. As another foundational model organism with abundant genomic information across many evolutionary lineages~\cite{Yang2018, Miller2018, Kim2021, Gramates2022}, the fruit fly, \textit{Drosophila melanogaster}, is a natural choice for subsequent investigation. Furthermore, given its complex multicellular development process and shared signaling pathways with humans, the findings of such a study would significantly advance our understanding of the role of IDRs in human health and disease. The concordance of these results with the previously identified IDR clusters would also have profound implications for the broader mechanisms of IDR evolution. For example, the absence of global patterns of evolutionary signatures across IDRs in \textit{Drosophila} would suggest they are property of IDRs which is unique to yeast. In contrast, the identification of clusters similar to those in yeast would indicate the existence of a taxonomy of IDRs which is conserved across the tree of life.
